What to simulate? Inferring the direction for mental rotation

### 2014-01-30 man/cogsci-2014/cogsci-2014.tex
Add psiTurk reference

In the following section, we formalize this rational analysis, and
propose four models of mental rotation: one based on the original
hypothesis by \citeA{Shepard1971}; two which are extensions of the
first, but with relaxes assumptions; and one based on the active
sampling appraoach.

@@

We recruited 247 participants on Amazon's Mechanical Turk. Each
participant was paid \$1.00 for approximately 15 minutes of work,
consisting of one block of 10 practice trials followed by two blocks
of 100 experiment trials. Within a block, trials were presented in a
random order.

>>>>

In the following section, we formalize this rational analysis, and
propose four models of mental rotation: one based on the original
hypothesis by \citeA{Shepard1971}; two which are extensions of the
first but with relaxed assumptions; and one based on the active
sampling approach.

@@

We recruited 247 participants on Amazon's Mechanical Turk using the
psiTurk experiment framework \cite{Mcdonnell12}. Each participant was
paid \$1.00 for approximately 15 minutes of work, consisting of one
block of 10 practice trials followed by two blocks of 100 experiment
trials. Within a block, trials were presented in a random order.
